\textbf{ \Large {Decentralized autonomous sensor fault detection using neural networks}}

### 2015-02-18 Paper/PaperJahrSchlich.tex
lab tests, mean error figure

%\begin{figure}[htbp]
%    \centering
%    \includegraphics[width = \textwidth]{figures/uml-basestation.pdf}
%    \caption{Class diagram of the \texttt{basestation} package}
%    \label{fig:UML-bs}
%\end{figure}

@@

In several test runs, the properties of the neural network are optimized.

has been tested with varying numbers of training measurements (\autoref{fig:traininputs}).
With increasing numbers of training measurement, the prediction accuracy increases.

The neural network has been validated by repeated tests---using varying excitation forces, varying sampling rates, and varying quantities of measured values.

The implementation of the FFT has been verified by plotting the frequency sprectrum of various vibration measurements, (\autoref{fig:76hzfft}).
The natural frequencies can be identified by the peaks in the magnitude graph.
Each sensor node stores the calculated first natural frequency and the corresponding magnitude in a \texttt{Measurement} object and transmits the object to the other sensor nodes.

\begin{itemize}
\item \textbf{neuronales Netz}
%\item TRAININGSPHASE
%\item Austausch der gemessenen FFT zwischen den Sensoren
%\item trainieren des neuronalen Netzes, bis keine Verbesserung bei Vorhersagegenauigkeit eintritt
%\item MESSPHASE
%\item Austausch der gemessenen FFT zwischen den Sensoren
%\item Nutzen des neuronalen Netzes, um eventuellen Fehler zu finden
\item KÜNSTLICHEN FEHLER ERZEUGEN
\item TABELLE MIT ERMITTELTEN / GEMESSENEN WERTEN; MIT / OHNE FEHLERN
\end{itemize}

%The neural network has been validated by repeated tests---using varying excitation forces, varying sampling rates, and varying quantities of measured values.

%After excitation, i.e. when the acceleration threshold is exceeded as detected by the sensor nodes, the sensor nodes automatically start measuring the acceleration.
%Each sensor node performs a FFT, once sufficient acceleration measurements have been collected.
%By applying the FFT, the acceleration measurements are converted into the vibration frequencies and the corresponding magnitudes of the structure \cite{rao2011fast}.

%\begin{figure}[htb]
%    \centering
%    \includegraphics{figures/76HzHalf.pdf}
%    \caption{frequency domain graph of the vibration}
%    \label{fig:76hzfft}
%\end{figure}

After the sensor fault detection, the \texttt{Measurement} objects of all sensor nodes ar transmitted to the basestation.
The values and detected sensor faults are stored in a MySQL database and availeble for further analysis.

%Example results are shown in \autoref{tab:lab-ex}.
%The identified magnitudes increase with ascending sensor node position from top to bottom, corresponding to the higher deflection at the top of the structure.
%
%\textit{Through FFT analysis of sampling events, the data traffic is decreased from 512 doubles per sampling event to two doubles per sampling event.
%A number stored in the used data format double occupies 8\,bytes of space.
%The data traffic is decreased by (512$-$2)$\times$8\,B\,=\,4080\,B\,=\,3,98\,MB per sampling event, decreasing data traffic by 99.6\,\%.}

%\begin{table}[hb]
%	\centering
%	\begin{tabular}{l l c c c}
%		\toprule
%		ID & Position & Magnitude & Natural frequency [Hz] & Sampling rate [Hz]\\ 
%		\midrule
%		1 & top & 3.78 & 2.2461 & 76\\ 
%		1 & middle & 3.23 & 2.2461 & 76\\ 
%		1 & bottom & 1.97 & 2.2461 & 76\\ 
%		\midrule	
%		2 & top & 5.74 & 2.2536 & 76\\  
%		2 & middle & 4.38 & 2.2536 & 76\\ 
%		2 & bottom & 2.55 & 2.2536 & 76\\
%		\midrule
%		3 & top & 8.20 & 2.2536 & 76\\
%		3 & middle & 6.35 & 2.2536 & 76\\ 
%		3 & bottom & 3.79 & 2.2536 & 76\\
%		\bottomrule
%	\end{tabular}
%	\caption{Natural frequencies of the test structure}
%	\label{tab:lab-ex}
%\end{table}

>>>>

\begin{figure}[htbp]
    \centering
    \includegraphics[width = \textwidth]{figures/uml-basestation.pdf}
    \caption{Class diagram of the \texttt{basestation} package}
    \label{fig:UML-bs}
\end{figure}

@@

The neural network has been tested with varying numbers of training measurements (\autoref{fig:traininputs}).
With increasing numbers of training measurements, the prediction accuracy of the expected magnitude increases.

\begin{figure}[htb]
    \centering
    %\includegraphics{figures/traininputs.pdf}
    \caption{correlation between number of traing measurements and mean error during collection phase}
    \label{fig:traininputs}
\end{figure}

To validate the autonomous sensor fault detection, a sensor fault was simulated by shifting and rotating one of the sensor nodes after completion of the training phase.
The expected magnitudes deviated from the measured magnitudes (\autoref{tab:sensorfault}.
The SHM system recognized the deviation and the boolean was set to "TRUE" accordingly.

\begin{table}[hb]
	\centering
	\caption{Deviation between measured magnitude and expected magnitude with and without simulated sensor faults}
	\begin{tabular}{c c c c}
		\toprule
		Sensor fault & Measured magnitude & Expected magnitude & Deviation [\%]\\ 
		\midrule
		  & 2.1502 & 2.1389 & 0.5292 \\
		FALSE & 2.0817 & 2.0890 & 0.3529 \\
		  & 1.8663 & 1.8631 & 0.1726 \\
		\midrule	
		 & 1.8161 & 2.0725 & 12.3715\\
		TRUE & 1.6665 & 1.9404 & 14.1156\\
		 & 1.8238 & 2.1687 & 15.9035\\
		\bottomrule
	\end{tabular}
	\label{tab:sensorfault}
\end{table}

Through the embedded FFT analysis of sampling events, the data traffic is decreased from 512 values per measurement and sensor node to 4 values per sampling event.
A number stored in the used data format double occupies 8\,bytes of space.
The data traffic is decreased by (512$-$4)$\times$8\,B\,=\,4064\,B\,=\,3.97\,MB per sampling event, decreasing data traffic by 99.3\,\%.
